\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-05 fully-abstract-comp/popl2019/paper.tex
Introduction to FAOS section.

\section{Formulating Security with a Fully Abstract Overlay Semantics}
\label{sec:form-secur-with}
\begin{figure}[htb]
  \centering
  \[
    \arraycolsep=1.4pt
    \begin{array}{rcl}
      \src{\SealableCaps} & \defbnf& \SealableCaps \mid \src{\stkptr{\permbnf,\basebnf,\aendbnf,\addrbnf}} \mid \src{\retptrd(\basebnf,\aendbnf)}\\
                          & &  \mid \src{\retptrc(\basebnf,\aendbnf,\addrbnf)}\\
      \multicolumn{3}{c}{
      \begin{array}{lcrclcr}
        \src{\StkFrame} & \defeq & \src{\Addr \times \MemSeg} & \phantom{skipskipsip} & \src{\Stack} & \defeq & \src{ \StkFrame^*}
      \end{array}
                                                                                                                }\\
      \src{\ExecConf} & \defeq & \Mem \times \Reg \; \src{\times \; \Stack \times \MemSeg} \\
    \end{array}
  \] 
\[
  \begin{array}{rcl}
    \offpc,\offsigma & \in & \nats \\
    \src{\Instr} & \defbnf &  \Instr \mid \scall{\offpc,\offsigma}{r}{r}
  \end{array}
\]
  \caption{The syntax of the capability machine with a built-in stack.}
  \label{fig:src-syntax}
\end{figure}

>>>>

\section{Formulating Security with a Fully Abstract Overlay Semantics}
\label{sec:form-secur-with}
A central contribution of this paper is to prove that \stktokens{} actually guarantees LSE and WBCF.
Our proof uses a novel approach called full abstract overlay semantics.
In this approach, we first define an overlay semantics for \trgcm{} which has LSE and WBCF by construction.
An overlay semantics is basically a different view on an existing semantics.
For instance, it may have new syntactic constructs and have special semantics for these things, but they will correspond to something on the underlying machine.
In the overlay semantics we are about to define for \trgcm{}, there is an explicit stack pointer construct on the machine, but on the underlying semantics the stack pointer corresponds directly to a linear capability for the part of memory the overlay semantics has deemed to be the stack.
When we have defined the overlay semantics, we prove full-abstractness for a compilation from the overlay semantics to the underlying semantics. 
Generally speaking, the compilation from an overlay semantics to an underlying semantics should be straightforward as it is really just a different view on the same thing. 
In this case, the compilation even turns out to be the identity function!
\todo[inline]{Maybe also introduce reasonability here}

\begin{figure}[htb]
  \centering
  \[
    \arraycolsep=1.4pt
    \begin{array}{rcl}
      \src{\SealableCaps} & \defbnf& \SealableCaps \mid \src{\stkptr{\permbnf,\basebnf,\aendbnf,\addrbnf}} \mid \src{\retptrd(\basebnf,\aendbnf)}\\
                          & &  \mid \src{\retptrc(\basebnf,\aendbnf,\addrbnf)}\\
      \multicolumn{3}{c}{
      \begin{array}{lcrclcr}
        \src{\StkFrame} & \defeq & \src{\Addr \times \MemSeg} & \phantom{skipskipsip} & \src{\Stack} & \defeq & \src{ \StkFrame^*}
      \end{array}
                                                                                                                }\\
      \src{\ExecConf} & \defeq & \Mem \times \Reg \; \src{\times \; \Stack \times \MemSeg} \\
    \end{array}
  \] 
\[
  \begin{array}{rcl}
    \offpc,\offsigma & \in & \nats \\
    \src{\Instr} & \defbnf &  \Instr \mid \scall{\offpc,\offsigma}{r}{r}
  \end{array}
\]
  \caption{The syntax of the capability machine with a built-in stack.}
  \label{fig:src-syntax}
\end{figure}
